Liveness-Based Garbage Collection for Lazy Languages

### 2015-07-10 paper/paper.tex
new graph

\subsection{Results}
\newcommand{\hgt}{3cm}
\begin{figure*}[t!]
\renewcommand{\arraystretch}{.1}
\begin{tabular}{@{}c@{}c@{}}
\hskip -4mm{\epsfig{file=sudoku.eps, height=\hgt}}%, width=4.10cm}}
&
{\epsfig{file=lcss.eps, height=\hgt}}%, width=4.10cm}}
\\
\hskip -4mm{\epsfig{file=gc_bench.eps, height=\hgt}}%
 &
{\epsfig{file=nperm.eps, height=\hgt}}%
\\
\hskip -4mm{\epsfig{file=fibheap.eps, height=\hgt}}%
&
{\epsfig{file=sudoku.eps, height=\hgt}}%%%Add knightstour.eps
\\
\hskip -4mm{\epsfig{file=nqueens.eps, height=\hgt}}%
&
{\epsfig{file=treejoin.eps, height=\hgt}}%
\end{tabular}\vskip -10mm
 \caption{Memory usage  snapshot of  programs.  The  blue and  the red
   curves indicate the  number of cons cells in  the active semi-space
   for  LGC and  RGC  respectively.  The  black  curve represents  the
   number of reachable cells and  the grey curve represents the number
   of cells that are actually live  (of which liveness analysis does a
   static approximation).  x-axis is  the time  measured in  number of
   cons-cells allocated (scaled down by  factor $10^5$). y-axis is the
   number of cons-cells (scaled down by factor $10^3$).}
\label{fig:memory-usage} \figrule
\end{figure*}

>>>>

\subsection{Results}
\newcommand{\hgt}{3cm}
\begin{figure*}[p]
\renewcommand{\arraystretch}{.1}
\begin{tabular}{@{}c@{}c@{}}
   \hskip -4mm{\epsfig{file=lambda.eps, height=\hgt}}
   & {\epsfig{file=lambda_win.eps, height=\hgt}}
\\ \hskip -4mm{\epsfig{file=lcss.eps, height=\hgt}}
&  \hskip -4mm{\epsfig{file=lcss_win.eps, height=\hgt}}
\\ \hskip -4mm{\epsfig{file=gc_bench.eps, height=\hgt}}
&  \hskip -4mm{\epsfig{file=gc_bench_win.eps, height=\hgt}}
\\ \hskip -4mm{\epsfig{file=nperm.eps, height=\hgt}}
&  \hskip -4mm{\epsfig{file=nperm_win.eps, height=\hgt}}
\\ \hskip -4mm{\epsfig{file=fibheap.eps, height=\hgt}}
&  \hskip -4mm{\epsfig{file=fibheap_win.eps, height=\hgt}}
\\ \hskip -4mm{\epsfig{file=sudoku.eps, height=\hgt}}
&  \hskip -4mm{\epsfig{file=sudoku_win.eps, height=\hgt}}
\\ \hskip -4mm{\epsfig{file=nqueens.eps, height=\hgt}}
&  \hskip -4mm{\epsfig{file=nqueens_win.eps, height=\hgt}}
\\ \hskip -4mm{\epsfig{file=treejoin.eps, height=\hgt}}
&  \hskip -4mm{\epsfig{file=treejoin_win.eps, height=\hgt}}
\end{tabular}\vskip -10mm
 \caption{Memory usage  snapshot of  programs.  The  blue and  the red
   curves indicate the  number of cons cells in  the active semi-space
   for  LGC and  RGC  respectively.  The  black  curve represents  the
   number of reachable cells and  the grey curve represents the number
   of cells that are actually live  (of which liveness analysis does a
   static approximation).  x-axis is  the time  measured in  number of
   cons-cells allocated (scaled down by  factor $10^5$). y-axis is the
   number of cons-cells (scaled down by factor $10^3$).}
\label{fig:memory-usage} \figrule
\end{figure*}
